\( \tool \): JavaScript IR-based Semantics Extraction Toolchain

### 2019-08-24 icse20/conclusion.tex
First submission

\section{Conclusion}\label{sec:conclude}
The annual updates of the ECMAScript specification makes it difficult to
build program analysis or formal verification of JavaScript due to the
required human efforts in modeling a moving target.  In this paper,
we proposed a tool \( \tool \), which \textit{automatically} extracts the
syntax and semantics specified in the ECMAScript specification.  The tool
generates a parser from a language grammar written in \( \bnfes \), and
compiles abstract algorithms written in English to \( \ires \) functions.
The only parts that require manual efforts are compile rules and
language-specific global setting, which we provide for ECMAScript
as an example case study.  We also support a rule assistant to guide
how to convert new abstract algorithms.  We evaluated \( \tool \) by
applying it to ECMAScript 2020 with Test262.  The extracted semantics
passed 19,220 of 19,282 applicable tests in Test262 and we showed
that the tool is also applicable to an incomplete language proposal as
a case study.  The tool also detected six confirmed errors from the
specification and the proposal. The implementation of the tool is
publicly available as an open-source project.

>>>>

\section{Conclusion}\label{sec:conclude}
The annual updates of the ECMAScript specification makes it difficult to
build program analysis or formal verification of JavaScript due to the
required human efforts in modeling a moving target.  In this paper,
we proposed a tool \( \tool \), which \textit{automatically} extracts the
syntax and semantics specified in the ECMAScript specification.  The tool
generates a parser from a language grammar written in \( \bnfes \), and
compiles abstract algorithms written in English to \( \ires \) functions.
The only parts that require manual efforts are compile rules and
language-specific global setting, which we provide for ECMAScript
as an example case study.  We also support a rule assistant to guide
how to convert new abstract algorithms.  We evaluated \( \tool \) by
applying it to ECMAScript 2020 with Test262.  The extracted semantics
passed 19,220 of 19,282 applicable tests in Test262 and we showed
that the tool is also applicable to an incomplete language proposal.
The tool also detected six confirmed errors from the
specification and the proposal.  The implementation of the tool is
publicly available as an open-source project.

### 2019-08-24 icse20/eval.tex
First submission

\subsection{Correctness}
\begin{table}[t]
  \centering
  \caption{Testing results of Test262 for ECMAScript 2020}
  \label{table:test262}
\vspace*{-.5em}
\small
  \begin{tabular}{lr}\toprule
    \belowrulesepcolor{gainsboro}
    \rowcolor{gainsboro} \textbf{All tests262 Tests} & \textbf{36,794}\\
    \aboverulesepcolor{gainsboro}\midrule
    Annexes/Internationalisation & 1,774\\\hdashline
    In-progress features & 5,895\\\midrule
    \belowrulesepcolor{gainsboro}
    \rowcolor{gainsboro} \textbf{ECMAScript 2020 Tests} & \textbf{29,125}\\
    \aboverulesepcolor{gainsboro}\midrule
    Non-strict mode tests & 1,136\\\hdashline
    Module tests& 918 \\\hdashline
    Early error tests & 1,316\\\hdashline
    Inessential built-in object tests & 6,473\\\midrule
    \belowrulesepcolor{gainsboro}
    \rowcolor{gainsboro} \textbf{Applicable Tests} & \textbf{19,282}\\
    \aboverulesepcolor{gainsboro}\midrule
    Passed tests & 19,220 \\\hdashline
    Failed tests & 62 \\\bottomrule
  \end{tabular}
\vspace*{-1em}
\end{table}

@@

We tested the interpreter using Test262, the official conformance test
suite provided by TC39, as of August 6, 2019.  Because Test262
contains tests for extensions and in-progress features, we excluded
them to focus on the semantics of ECMAScript 2020.  As Table~\ref{table:test262} shows,
Test262 consists of 36,794 tests and we excluded 7,669 tests for
extensions and in-progress features.  We also filtered out
tests for excluded features described in Section~\ref{sec:impl}.
Finally, we tested 19,282 applicable tests with our JavaScript
interpreter and only 62 tests are failed. Among them, 54 tests
utilize implementation-dependent features and 3 tests are timeout
and 5 tests are wrong tests. Thus, we believe that all the
semantics extracted from \( \tool \) are correct.

>>>>

\subsection{Correctness}
\begin{table}[t]
  \centering
  \caption{Testing results of Test262 for ECMAScript 2020}
  \label{table:test262}
\vspace*{-.5em}
\footnotesize
  \begin{tabular}{lr}\toprule
    \belowrulesepcolor{gainsboro}
    \rowcolor{gainsboro} \textbf{All Test262 Tests} & \textbf{36,794}\\
    \aboverulesepcolor{gainsboro}\midrule
    Annexes/Internationalisation & 1,774\\\hdashline
    In-progress features & 5,895\\\midrule
    \belowrulesepcolor{gainsboro}
    \rowcolor{gainsboro} \textbf{ECMAScript 2020 Tests} & \textbf{29,125}\\
    \aboverulesepcolor{gainsboro}\midrule
    Non-strict mode tests & 1,136\\\hdashline
    Module tests& 918 \\\hdashline
    Early error tests & 1,316\\\hdashline
    Inessential built-in object tests & 6,473\\\midrule
    \belowrulesepcolor{gainsboro}
    \rowcolor{gainsboro} \textbf{Applicable Tests} & \textbf{19,282}\\
    \aboverulesepcolor{gainsboro}\midrule
    Passed tests & 19,220 \\\hdashline
    Failed tests & 62 \\\bottomrule
  \end{tabular}
\vspace*{-1em}
\end{table}

@@

We tested the interpreter using Test262, the official conformance test
suite provided by TC39, as of August 6, 2019.  Because Test262
contains tests for extensions and in-progress features, we excluded
them to focus on the semantics of ECMAScript 2020.  As Table~\ref{table:test262} shows,
Test262 consists of 36,794 tests and we excluded 7,669 tests for
extensions and in-progress features.  We also filtered out
tests for excluded features described in Section~\ref{sec:impl}.
Finally, we tested 19,282 applicable tests and only 62 tests failed.
Among them, 54 tests utilize implementation-dependent features,
three are timeout with 20 minutes due to enormous computation,
and five are wrong tests.  Thus, we believe that all the
semantics extracted from \( \tool \) are correct.

### 2019-08-24 icse20/impl.tex
First submission

\section{Implementation}\label{sec:impl}
This section describes the implementation detail of our open-source
tool, \( \tool \)\footnote{The URL of the tool is anonymized due to a
double-blind review process.}.  We target
%aim to extract the syntax and semantics from 
ECMAScript 2020, which is actively updated in its
GitHub repository~\cite{es2020} to be released in the next year.

@@

\paragraph{Non-Strict Mode}
Since ECMAScript 5, JavaScript introduced strict mode to
\textit{intentionally} provide slightly different semantics.  It
provides more stable semantics by preventing unsafe actions or
throwing originally ignored errors.  However, the ECMAScript
specification states that ``Strict mode does not restrict or modify
any aspect of the ECMAScript semantics that must operate consistently
across multiple source text units.''  Thus, we decided to support only
strict mode to focus on the main contribution of this paper.

\paragraph{Modules}
Moreover, we do not support modules that were introduced since ES6
(ECMAScript 2015).  With the \( \code{import} \) keyword, a JavaScript
program can import other JavaScript components defined with the \(
\code{export} \) keyword in their modules.  In order to support
modules in our automatically generated semantics, we should model the
functionality to communicate with file systems to access JavaScript
module files.  Because modules do not affect the overall JavaScript
semantics critically, we decided not to support modules.

\paragraph{Inessential Built-in Objects}
JavaScript provides various standard built-in objects to support
helper functions.  However, several built-in libraries are not essential
to the core JavaScript semantics but support extra functionalities such as
\( \code{Math} \), \( \code{Date} \), \( \code{RegExp} \), and
\( \code{JSON} \).  Thus, we decided not to support such libraries
following the tradition of KJS~\cite{kjs}, which is a complete
formal semantics of JavaScript.

@@

\paragraph{ECMAScript Data Types}
In ECMAScript 2020, Section 6 \textsf{ECMAScript Data Types and Values}
describes data types used in the specification.  It describes not only
data types explicitly exposed for JavaScript evaluation, but also all
the internal data types used in the specification.  For example, the
Environment Records are record types from identifiers to bindings for
values.  They are not explicitly accessible in JavaScript programs
but defined and used internally in the specification.

>>>>

\section{Implementation}\label{sec:impl}
We describe the implementation detail of our open-source
tool, \( \tool \)\footnote{The URL of the tool is anonymized due to a
double-blind review process.}, which targets
ECMAScript 2020~\cite{es2020}.

%We describe how we implement an open-source \( \tool \)\footnote{
%The URL of the tool is anonymized due to a double-blind review process.},
%which targets ECMAScript 2020~\cite{es2020}.

@@

\vspace*{-.5em}
\paragraph{Non-Strict Mode}
Since ECMAScript 5, JavaScript introduced strict mode to
provide different semantics.  It
provides more stable semantics by preventing unsafe actions or
throwing originally ignored errors.  However, the ECMAScript
specification states that ``Strict mode does not restrict or modify
any aspect of the ECMAScript semantics that must operate consistently
across multiple source text units.''  Thus, we decided to support only
strict mode.

\vspace*{-.5em}
\paragraph{Modules}
Moreover, we do not support modules that were introduced since ES6.
With the \( \code{import} \) keyword, a JavaScript
program can import other JavaScript components.  To support
modules in our automatically generated semantics, we should model the
functionality to communicate with file systems to access JavaScript
module files.  Because modules do not affect the overall JavaScript
semantics critically, we decided not to support modules.

\vspace*{-.5em}
\paragraph{Early Errors}
ECMAScript specifications use Early Error Rules to preclude invalid code
before evaluation. For example, an Early Error Rule checks whether
functions have duplicated parameters in strict mode.
Because they are written in differenet styles from abstract algorithms,
we do not support Early Error Rules.

\vspace*{-.5em}
\paragraph{Inessential Built-in Objects}
JavaScript provides various standard built-in objects but some of them
are not essential to core JavaScript but support extra functionalities such as
\( \code{RegExp} \) and \( \code{JSON} \).  Thus, we decided not to
support such libraries following the tradition of KJS~\cite{kjs},
which is a complete formal semantics of JavaScript.

@@

\vspace*{-.5em}
\paragraph{ECMAScript Data Types}
In ECMAScript 2020, Section 6 \textsf{ECMAScript Data Types and Values}
describes data types used in the specification.  It describes not only
data types explicitly exposed for JavaScript evaluation, but also all
the internal data types used in the specification.  For example, the
Environment Records are record types from identifiers to bindings for
values.  They are not explicitly accessible in JavaScript programs
but defined and used internally in the specification.
